Measurement and Probability in Fuzzy Quantum Theories

### 2016-12-04 prop.tex
prop.tex \section{Conclusion and Discussion} Update table title...

given more and more resources. In particular, we could summarize our
examples and Gleason's theorem in table~\ref{table_long}. 

@@

\end{tabular}}\caption{Summarize example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value}
and Gleason's theorem}

>>>>

given more and more resources. In particular, we could summarize example~\ref{ex:three-dimensional-three-value}
and \ref{ex:three-dimensional-4-value} and Gleason's theorem in table~\ref{table_long}.

@@

\end{tabular}}\caption{How measurement resources effect identifying states from interval-valued
probability measures.}
